A flexible and intuitive analytic expression for the metallicity-dependent cosmic star formation rate

### 2022-07-04 src/tex/ms.tex
[showyourwork] overleaf sync

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Abstract with filler text
\begin{abstract}
New observational facilities are probing astrophysical transients such as gravitational wave (GW) sources at ever increasing redshifts. To interpret these observation we need to compare them to predictions from stellar population models. These models are very sensitive to the metallicity-dependent star formation rate density (\SFRDzZ). 
% Large uncertainties remain in the value and shape of the \SFRDzZ, especially at the low metallicities that are crucial to the formation of GW events.
Understanding the behaviour of the adopted \SFRDzZ is essential to explain simulation results. 
%
% Various approaches to approximate \SFRDzZ exist, ranging from fully empirical prescriptions to prescriptions that are based on cosmological simulations.
In this work, we propose a simple analytical form for \SFRDzZ. The novelty of this model lies in a skewed-lognormal distribution of metallicities, that captures the tail of low metallicity star formation at low redshift. 
Variations of this analytical form can be easily interpreted, because the parameters are intuitively linked to the shape of \SFRDzZ. %Our hope is that this expression provides a useful starting point for making predictions and comparison with observations.
%
We fit our analytical form to the starforming gas of the cosmological TNG100 simulations and find our model is able to capture the main behaviour. 
%
As an example, we investigate the effect of systematic variations in the \SFRDzZ parameters on the predicted mass distribution of locally merging binary black holes (BBH). Our main findings are I) the low mass end is least affected by variations in \SFRDzZ, II) the distribution of metallicities at low redshift affects the normalisation of of the BBH merger rate, while III) the redshift evolution of the metallicity distribution affects the slope of the mass distribution beyond the peak value. 
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction \label{sec: intro}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
A myriad of astrophysical phenomena depend critically on the rate of star formation throughout the cosmic history of the Universe. Transient phenomena, including core collapse supernovae, (pulsational) pair-instability supernovae, long gamma-ray bursts and gravitational wave (GW) events are particularly sensitive to the metallicity at which star formation occurs at different epochs throughout the Universe.
In particular, the field of gravitational astronomy has seen explosive growth in the past decade \citep[][]{GWTC1,GWTC2,GWTC3}. In order to correctly model and interpret these observations, it is fundamental to know rate of star formation at different metallicities throughout cosmic history, i.e. the metallicity-dependent star formation rate density \SFRDzZ \citep[see also the recent review by][]{chruslinska2022_review}.

It is difficult to observationally constrain the shape of \SFRDzZ (see \cite{Chruslinska2019_obs} for an extensive overview and discussion of relevant observational caveats). Even at low redshifts, the low metallicity part of the distribution is poorly constrained \citep{Chruslinska+2021}.
Traditionally the metallicity density distribution is estimated by combining a mass-metallicity relation (MZ-relation) and a galaxy stellar mass function (GSMF) \citep[see also][]{Chruslinska+2018, Chruslinska2019_effectCO, Broekgaarden+2021a}.
Another way is to extract the metallicity density fraction from cosmological simulations \citep[e.g.]{Mapelli2017, Schneider+2017}
Alternatively, one can combine an observed star formation rate, \SFRDz, like from \cite{MadauDickinson2014} or \cite{Madau+2017}, and convolve this with some belief about the shape of the metallicity density distribution, such as was was done in \cite{Neijssel+2019}.
A third option is extract this information from cosmological simulations \citep[e.g.][]{Mapelli+2017,Schneider+2017}.
In this work we provide an analytical model which we fit to the \SFRDzZ based on the TNG 100 simulation \citep{Pillepich2018, Weinberger2017}.

% Large uncertainties exist in the shape and redshift evolution of both \SFRDz, and the cosmic distribution of metallicities \dpdZ (see e.g. \citealt{Chruslinska2019_obs}, \citealt{Boco2021} and \citealt{Chruslinska+2021} for an extended discussion on the metallicity dependent star formation rate density, in light of empirical data).

% To construct \SFRDzZ from empirical data, one can estimate \dpdZ by combining observed mass-metallicity relations with galaxy stellar mass functions \citep[see e.g.][]{Chruslinska+2018, Chruslinska2019_obs, Broekgaarden+2021b}. Alternatively, one could extract \SFRDzZ directly from cosmological simulations \citep[e.g.][]{Mapelli2017, Briel+2021}.

% \citet{Mapelli2017} and \cite{Briel+2021}  but instead of directly extracting the \SFRDzZ from a cosmological simulation

% we take an approach similar to \cite{LangerNorman}, but instead of following the observed mean metallicity with redshift, we fit our combined analytical representations of \SFRDz and \dpdZ to simulation data.

In this work, we present a convenient flexible model for the \SFRDzZ that can be fit to both simulation and observational data. By adopting an analytical, parametrized form for \SFRDzZ, the large uncertainties in \SFRDzZ can be systematically explored through smoothly varying the parameters that control its shape.

We describe our model for \SFRDzZ in Section \ref{sec: model for sfrd(zZ)}.
We fit our model to to the starforming gas in the illustris TNG simulation in Section \ref{sec: fit against tng}. In Section \ref{sec: mass dists} we demonstrate an example application of our model by systematically varying the parameters that determine the shape of \SFRDzZ and investigate their impact on the local distribution of merging BBH masses.
We summarise in Section \ref{sec: summary}.

@@

% $a=0.02$, $b=1.48$, $c=4.45$ and $d=5.9$ as best fitting parameters,
\subsection{The metallicity probability density function}
For the probability distribution of metallicities we draw inspiration from the approach by \citep[e.g.\ ][]{Neijssel+2019} who used a log-normal distribution. Unfortunately, this expression does not capture the asymmetry well that we see in the results of the cosmological simulations, which show an extended tail towards low metallicity combined with a very limited tail towards higher metallicity, when plotted as a function of $\log_10 Z$. To capture this behavior we adopt a skewed-log-normal distribution instead. This is an extension of the normal distribution that introduces an additional shape parameter, $\alpha$, that regulates the skewness \citep{Ohagan+1976}. This allows us to more accurately capture the asymmetry in the metallicity distribution at each redshift.

@@

\noindent For the evolution of the mean metallicity with redshift we follow \cite{Neijssel+2019} and \cite{Langer2006} in assuming that the mean of the probability density function of metallicities evolves with redshift as:
\begin{equation}
\label{eq: mean Z}
    \langle Z \rangle \equiv \mu(z) = \mu_0 \cdot 10^{\mu_z \cdot z},
\end{equation}
where $\mu_0
%= 0.025 
$ is the mean metallicity at redshift 0, and $\mu_z
%= -0.048
$ determines redshift evolution of the location. Equating this to Equation~\ref{eqn:Zmean}, we get an expression for $\xi(z)$,

@@

We will also allow the ``scale'' $w$ also evolves with redshift in a similar manner, 
\begin{equation}
\label{eq: sigma z}
    \omega(z) = \omega_0 \cdot 10^{\omega_z \cdot z}.
\end{equation}
where $\omega_0$ is
%$\omega_0 = 1.125$, 
the width of the metallicity distribution at $z=0$, and $\omega_z$
%$\omega_z = 0.048$, 
the redshift evolution of the scale.

@@

\subsection{The overall cosmic star formation rate density}
For the star formation rate density, we assume the analytical form proposed by \cite{MadauDickinson2014},
\begin{eqnarray}
\label{eq: sfr1}
\boxed{
    \SFRDz  = 
    \frac{d^2 M_{\rm SFR}}{dt dV_c} (z)= 
    a \frac{\left(1 + z\right)^b}{1 + \left[ (1 + z)/c \right]^d} 
    }\,
\end{eqnarray}
in units of $\left[ \Msun \,yr^{-1} \,cMpc^{-3} \right]$. This introduces four parameters, $a$ which sets the overal normalisation and which has the same units as \SFRDz and $b,c$ and $d$ which are unitless and which govern the shape of the overal cosmic star formation rate density with redshift. \\

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\script{FitComparison_3panelPlot.py}
\includegraphics[width=0.9\textwidth]{figures/SFRD_FIT_evaluation_compare.pdf}
\caption{Our fiducial \SFRDzZ model, adopting the best fitting parameters (listed on the top right) to fit the TNG100 simulations.
The top panel shows the full two dimensional \SFRDzZ linear in time. The bottom left (right) panel shows slices of the distribution in redshift (metallicity). Each slice is displaced by 0.01$\Msun \yr^{-1}\Mpc^{-3}$. We show the TNG100 simulation data with thick gray lines. 
For comparison, we also show the phenomenological model from \protect\cite{Neijssel+2019} in each panel with grey dotted lines. For the latter, the contours in the top panel range from $10^{-7} - 10^{-2} \Msun \yr^{-1}\Mpc^{-3}$. This shows that our analytical model adequately captures the \SFRDzZ of the TNG100 simulations.
 \label{fig: fit SFRD}}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We fit our newly defined functional form of \SFRDzZ as defined by equations \ref{eq: total sfrd}, \ref{eq: z log skew} and \ref{eq: sfr1} to the Illustris-TNG cosmological simulations. 
We fit for the following nine free parameters $\alpha, \mu_0, \mu_z, \omega_0, \omega_z$, which govern the metallicity dependence and $a,b, c$ and $d$, which set the overall star formation rate.

@@

% %
% The task we have at hand here is not a standard textbook fitting problem given the specific aims and requirements that we have that are driven by the astrophysical applications we have in mind. Qualitatively, our aims are the following. Our main aim is to find solution for the free parameters, for which the expression reproduces the overall behaviour that is observed in the cosmological simulations. For the purposes we have in mind, it will be more important to prioritise fitting the large scale trends, while we are not so interested in smaller scale fluctuations. We further prioritise getting the bulk of the cosmic star formation right and are less interested in capturing the behaviour in metallicity and redshift bins where the cosmic star formation rate is very low and thus insignificant for the overall picture. Finally, we are especially interested in capturing the asymmetry of the metallicity distribution. 
% There is not one unique procedure that will full fill these criteria.  After experimenting with different criteria we have adopted the procedure below, which we believe works well for the aims we have in mind.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Illustris-TNG Cosmological simulations}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The IllustrisTNG-project \citep[or TNG in short][]{FirstResTNG_Springel2018,FirstResTNG_Marinacci2018, FirstResTNG_Nelson2018,FirstResTNG_Pillepich2018, FirstResTNG_Naiman2018} considers galaxy formation and evolution through large-scale cosmological hydrodynamical simulations.
Such simulations provide the tools to study parts of the Universe that are not easily accessible by observations. In particular of interest for this work, they simulate the high redshift enrichment of galaxies and the tail of low metallicity star formation at low redshift.

Different cosmological simulations produce varying \SFRDzZ, depending on the adopted assumptions about the creation and distribution of metals. For a detailed discussion of the processes that govern the creation, distribution and mixing of metals in in the TNG simulations we refer to \cite{Pakmor+2022}.
We have chosen to fit of our analytical model to the illustris simulations because I) they have been shown to reproduce many of the global properties of galaxies and their scaling relations for a representative portion of the Universe \citep[e.g.][]{FirstResTNG_Naiman2018,Torrey+2021,Genel+2018,Hemler+2021}. 
II) \cite{Briel+2021} find that the \SFRDzZ from the EAGLE \citep{Schaye+2015,Crain+2015} and TNG simulations provide the best agreement between observed and predicted cosmic rates for electromagnetic and gravitational-wave transients. And III) the simulation output is publicly available.\footnote{ \url{https://www.tng-project.org/}} 
Although in this work, we only fit our model to the IllustrisTNG100 simulation, our prescription can be easily be used to fit other observational or simulated data of the metallicity dependent star formation rate density.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Choices and binning of the data}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We fit equation \ref{eq: total sfrd} to the metallicity-dependent star formation rate of the starforming gas in the TNG100 simulation. For this we use a binned version of the TNG data $\SFRDzZ_{\rm sim}$. We consider metallicities between $Z= -5$ to $\log_{10} Z= 0$ in 30 bins, where we use $Z_i$ to refer to the logarithmic centers of the bins. We ignore star formation in metallicities $\log_{10} Z \le -5$ as this accounts for less than 1\% of the total cosmic star formation rate in these simulations.
We consider bins in redshifts between $z=0$ and $z=10$, with a step size of $dz=0.05$, where $z_j$ refers to the centers of the bins.

@@

Subsequently we sum the $\chi^2 (z_j)$ for all redshift bins $z_j$. To ensure that our fit procedure gives sufficient weight to the behaviour at all redshifts, we find that we need to introduce a penalisation factor to somewhat reduce the contribution of redshifts where the peak of cosmic star formation occurs, while increasing the weight where at redshifts where the overal cosmic star formation rate is lower.  To achieve this we divide $\chi^2 (z_j)$ by the star formation $\sum_{Z_i} \mathcal{S}(Z_i,z_j)$ per redshift bin before adding the contribution of all redshifts.  Our final expression for the cost function reads

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Resulting \SFRDzZ}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Our best fitting parameters are listed in Table \ref{tab: fit params}. With these fit parameters, $\chi^2(z_j)$ is smaller than $2\cdot 10^{-4}$ at any given redshift. We will refer to the \SFRDzZ with the parameters listed in Table \ref{tab: fit params} as our fiducial \SFRDzZ model. 
% With the fit parameters as mentioned above, we find a maximum residual between the model and the TNG100 data of $2.3\cdot 10^{-3} \Msun \yr^{-1} \Mpc^{-3}$ at any given redshift.

@@

In Figure \ref{fig: fit SFRD} we show our fiducial \SFRDzZ model at different redshifts and metallicities. For clarity, we also show the overal rate of star formation \SFRDz in Figure \ref{fig: SFR(z)}.
In general, our analytical model captures the metallicity dependent star formation in the TNG100 simulations well (bottom panels of Figure \ref{fig: fit SFRD}). 
The skewed-log normal metallicity distribution is able to reproduce the overall behaviour that is observed in TNG100 \citep[bottom left panel, but cf. ][for an in-depth discussion of low metallicity star formation in the TNG50 simulation]{Pakmor+2022}
Only minor features like the additional bump just above $\log_{10}(Z) = -2$ at redshift 2 are missed. 
However, for our purposes, it is more important to prioritise fitting the large scale trends, while we are not so interested in smaller scale fluctuations.

Adopting a skewed-lognormal metallicity distribution allows for a tail of low metallicity star formation out to low redshifts. To emphasise the difference between a skewed-lognormal and a symmetric lognormal distribution, we show the phenomenological model from \cite{Neijssel+2019} in dotted grey. Their model falls within the family of functions that is encompassed by our model described in Section \ref{sec: model for sfrd(zZ)}. \footnote{The phenomenological model from \cite{Neijssel+2019} is recovered by adopting $\mu_0= 0.035$, $\mu_z=-0.23$, $\omega_0=0.39 $, $\omega_z = 0$, $\alpha = 0$, $a=0.01$, $b=2.77$, $c=2.9$ and $d=4.7$. }
The \SFRDzZ from \cite{Neijssel+2019} was optimised to match the local rate of double compact object mergers as presented in the second gravitational-wave catalogue. However, the resulting symmetric distribution cuts-off virtually all low-metallicity ($Z\leq 10^{-2.5}$) star formation.
% For both \SFRDzZ distributions, most star formation happens at metallicities above $Z \geq 10^{-2}$ (top panel).

@@

% The paramters that affect the redshift evolution change the slope of high mass BHs
Parameters that change the evolution of the metallicity distribution \dpdZ with redshift, such as $\omega_z$ and $\mu_z$ (top right and centre right panel), primarily affect the slope of the high mass end of the BBH mass distribution.
The difference between the effect on the low mass end with respect to the high mass end of the mass distribution is largest for these variations.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Abstract with filler text
\begin{abstract}
New observational facilities are probing astrophysical transients such as gravitational wave (GW) sources at ever increasing redshifts. To interpret these observation we need to compare them to predictions from stellar population models. These models are very sensitive to the metallicity-dependent star formation rate density (\SFRDzZ). 
% Large uncertainties remain in the value and shape of the \SFRDzZ, especially at the low metallicities that are crucial to the formation of GW events.
Understanding the behaviour of the adopted \SFRDzZ is essential to explain simulation results. 
%
% Various approaches to approximate \SFRDzZ exist, ranging from fully empirical prescriptions to prescriptions that are based on cosmological simulations.
In this work, we propose a simple analytical form for \SFRDzZ. 
The novelty of this model lies in a skewed-lognormal distribution of metallicities, that captures the tail of low metallicity star formation at low redshift. 
Variations of this analytical form can be easily interpreted, because the parameters are intuitively linked to the shape of \SFRDzZ. %Our hope is that this expression provides a useful starting point for making predictions and comparison with observations.
%
We fit our analytical form to the star-forming gas of the cosmological TNG100 simulations and find that it is able to capture the main behaviour well. 
%
As an example application, we investigate the effect of systematic variations in the \SFRDzZ parameters on the predicted mass distribution of locally merging binary black holes (BBH). Our main findings are I) the low mass end is least affected by variations in \SFRDzZ, II) the distribution of metallicities at low redshift affects the normalisation of of the BBH merger rate, while III) the redshift evolution of the metallicity distribution affects the high-mass slope of the mass distribution and IV) the shape of the overall star-formation rate has a small impact on the local mass distribution.
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction \label{sec: intro}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
A myriad of astrophysical phenomena depend critically on the rate of star formation throughout the cosmic history of the Universe. Transient phenomena, including core collapse supernovae, (pulsational) pair-instability supernovae, long gamma-ray bursts and gravitational wave (GW) events are especially sensitive to the metallicity at which star formation occurs at different epochs throughout the Universe.
Gravitational astronomy in particular has seen explosive growth in the number of detections in the past decade \citep[][]{GWTC1,GWTC2,GWTC3}. In order to correctly model and interpret these observations, it is fundamental to know the rate of star formation at different metallicities throughout cosmic history, i.e. the metallicity-dependent star formation rate density \SFRDzZ \citep[see also the recent review by][]{chruslinska2022_review}.

It is difficult to observationally constrain the shape of \SFRDzZ (see \cite{Chruslinska2019_obs} for an extensive overview and discussion of relevant observational caveats). Even at low redshifts, the low metallicity part of the distribution is poorly constrained \citep{Chruslinska+2021}.
Nonetheless, several methods exist to estimate the metallicity dependent star-formation rate. The first method combines a mass-metallicity relation (MZ-relation) and a galaxy stellar mass function (GSMF) \citep[see e.g.][]{Chruslinska+2018, Chruslinska2019_effectCO, Broekgaarden+2021a}.
Another way is to directly extract the metallicity density fraction from cosmological simulations \citep[e.g.]{Mapelli2017, Briel+2021}.
Alternatively, one can combine an observed star formation rate, \SFRDz, like from \cite{MadauDickinson2014} or \cite{Madau+2017}, and convolve this with some belief about the shape of the metallicity density distribution, such as was was done in \cite{Neijssel+2019}.

%Arguments: cosmological simulations work at high z,  but are they real? observations 
In this work we follow the latter approach and propose a flexible analytical model for the \SFRDzZ that can be fit to the output of both cosmological simulations, and observational data constraints where available. The novelty of this model lies in a skewed-lognormal distribution of metallicities, that captures the tail of low metallicity star formation at low redshift. 
The purpose of this model is to allow for an intuitive interpretation of the effects of the \SFRDzZ on the inferred rates of astrophysical transients. By adopting an analytical, parametrized form for \SFRDzZ, the large uncertainties in \SFRDzZ can be systematically explored.% through varying the parameters that control its shape.

We describe our model for \SFRDzZ in Section \ref{sec: model for sfrd(zZ)}.
We fit our model to to the star-forming gas in the Illustris TNG100 simulation in Section \ref{sec: mass dists} we demonstrate an example application of our model by systematically varying the parameters that determine the shape of \SFRDzZ and investigate their impact on the local distribution of merging BBH masses.
We summarise our findings in Section \ref{sec: summary}.

% %
% The task we have at hand here is not a standard textbook fitting problem given the specific aims and requirements that we have that are driven by the astrophysical applications we have in mind. Qualitatively, our aims are the following. Our main aim is to find solution for the free parameters, for which the expression reproduces the overall behaviour that is observed in the cosmological simulations. For the purposes we have in mind, it will be more important to prioritise fitting the large scale trends, while we are not so interested in smaller scale fluctuations. We further prioritise getting the bulk of the cosmic star formation right and are less interested in capturing the behaviour in metallicity and redshift bins where the cosmic star formation rate is very low and thus insignificant for the overall picture. Finally, we are especially interested in capturing the asymmetry of the metallicity distribution. 
% There is not one unique procedure that will full fill these criteria.  After experimenting with different criteria we have adopted the procedure below, which we believe works well for the aims we have in mind.  
%%
% Large uncertainties exist in the shape and redshift evolution of both \SFRDz, and the cosmic distribution of metallicities \dpdZ (see e.g. \citealt{Chruslinska2019_obs}, \citealt{Boco2021} and \citealt{Chruslinska+2021} for an extended discussion on the metallicity dependent star formation rate density, in light of empirical data).

% To construct \SFRDzZ from empirical data, one can estimate \dpdZ by combining observed mass-metallicity relations with galaxy stellar mass functions \citep[see e.g.][]{Chruslinska+2018, Chruslinska2019_obs, Broekgaarden+2021b}. Alternatively, one could extract \SFRDzZ directly from cosmological simulations \citep[e.g.][]{Mapelli2017, Briel+2021}. 
% \citet{Mapelli2017} and \cite{Briel+2021}  but instead of directly extracting the \SFRDzZ from a cosmological simulation 
% we take an approach similar to \cite{LangerNorman}, but instead of following the observed mean metallicity with redshift, we fit our combined analytical representations of \SFRDz and \dpdZ to simulation data.

@@

% $a=0.02$, $b=1.48$, $c=4.45$ and $d=5.9$ as best fitting parameters,
\subsection{The metallicity probability density function}
For the probability distribution of metallicities we draw inspiration from the approach by \citep[e.g.\ ][]{Neijssel+2019} who used a log-normal distribution. Unfortunately, this expression does not capture the asymmetry well that we see in the results of the cosmological simulations, which show an extended tail towards low metallicity combined with a very limited tail towards higher metallicity, when plotted as a function of $\log_{10} Z$. To capture this behavior we adopt a skewed-log-normal distribution instead. This is an extension of the normal distribution that introduces an additional shape parameter, $\alpha$, that regulates the skewness \citep{Ohagan+1976}. %This allows us to more accurately capture the asymmetry in the metallicity distribution at each redshift.

@@

\noindent For the evolution of the mean metallicity with redshift we follow \cite{Langer2006} and \cite{Neijssel+2019} in assuming that the mean of the probability density function of metallicities evolves with redshift as:
\begin{equation}
\label{eq: mean Z}
    \langle Z \rangle \equiv \mu(z) = \mu_0 \cdot 10^{\mu_z \cdot z},
\end{equation}
where $\mu_0
%= 0.025 
$ is the mean metallicity at redshift 0, and $\mu_z
%= -0.048
$ determines redshift evolution of the location. Equating this to Equation~\ref{eqn:Zmean}, we get an expression for $\xi(z)$,

@@

We will also allow the ``scale'' $\omega$ to evolve with redshift in a similar manner, 
\begin{equation}
\label{eq: sigma z}
    \omega(z) = \omega_0 \cdot 10^{\omega_z \cdot z}.
\end{equation}
where $\omega_0$ is
%$\omega_0 = 1.125$, 
the width of the metallicity distribution at $z=0$, and $\omega_z$
%$\omega_z = 0.048$, 
the redshift evolution of the scale.

@@

\subsection{The overall cosmic star formation rate density}
For the star formation rate density, we assume the analytical form proposed by \cite{MadauDickinson2014},
\begin{eqnarray}
\label{eq: sfr1}
\boxed{
    \SFRDz  = 
    \frac{d^2 M_{\rm SFR}}{dt dV_c} (z)= 
    a \frac{\left(1 + z\right)^b}{1 + \left[ (1 + z)/c \right]^d} 
    }\,
\end{eqnarray}
in units of $\left[ \Msun \,yr^{-1} \,cMpc^{-3} \right]$. This introduces four parameters; $a$ which sets the overal normalisation and which has the same units as \SFRDz and $b,c$ and $d$ which are unitless and which govern the shape of the overal cosmic star formation rate density with redshift. \\

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\script{FitComparison_3panelPlot.py}
\includegraphics[width=0.9\textwidth]{figures/SFRD_FIT_evaluation_compare.pdf}
\caption{Our fiducial \SFRDzZ model, adopting the best fitting parameters (listed on the top right) to fit the TNG100 simulations.
The top panel shows the full two dimensional \SFRDzZ linear in time. The bottom left (right) panel shows slices of the distribution in redshift (metallicity). Each slice is displaced by 0.01$\Msun \yr^{-1}\Mpc^{-3}$. We show the TNG100 simulation data with thick gray lines. 
For comparison, we also show the phenomenological model from \protect\cite{Neijssel+2019} in each panel with grey dotted lines. For the latter, the contours in the top panel range from $10^{-7} - 10^{-2} \Msun \yr^{-1}\Mpc^{-3}$. This shows that our analytical model adequately captures the \SFRDzZ of the TNG100 simulations.
 \label{fig: fit SFRD}}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We fit our new functional form of \SFRDzZ as defined by equations \ref{eq: total sfrd}, \ref{eq: z log skew} and \ref{eq: sfr1} to the Illustris-TNG cosmological simulations. 
We fit for the following nine free parameters $\alpha, \mu_0, \mu_z, \omega_0, \omega_z$, which govern the metallicity dependence and $a,b, c$ and $d$, which set the overall star formation rate.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Illustris-TNG Cosmological simulations}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The IllustrisTNG-project \citep[or TNG in short][]{FirstResTNG_Springel2018,FirstResTNG_Marinacci2018, FirstResTNG_Nelson2018,FirstResTNG_Pillepich2018, FirstResTNG_Naiman2018} considers galaxy formation and evolution through large-scale cosmological hydrodynamical simulations.
Such simulations provide the tools to study parts of the Universe that are not easily accessible by observations. In particular of interest for this work, they simulate the high redshift enrichment of galaxies and the tail of low metallicity star formation at low redshift.
Different cosmological simulations produce varying \SFRDzZ, depending on the adopted assumptions about the creation and distribution of metals.

The models implemented in the publicly available TNG simulations\footnote{ \url{https://www.tng-project.org/}} have lead to many successes. For a more extended discussion focused on the processes that govern the creation, distribution and mixing of metals in in the TNG simulations we refer to \cite{Pakmor+2022}. In short, star formation in the TNG simulations is calibrated against the Kennicutt–Schmidt relation \citep[][]{Schmidt1959,Kennicutt1989}. The stellar metallicity yields are and updated version of the original Illustris simulations as described in \cite{Pillepich2018}. Star particles deposit metals into the gas through Type Ia and Type II supernovae, as well as through Asymptotic Giant Branch mass loss. 
% Positives on TNG
The TNG simulations have been shown to match observational constraints on the mass-metallicity relation of galaxies up to $z = 2$ \citep{Torrey+2019}, as well as iron abundances \citep{FirstResTNG_Naiman2018} and the metallicity gradients within galaxies at low redshift \citep{Hemler+2021}. %They reproduce the evolution of the sizes of galaxies with redshift \citep{Genel+2018}   
Several studies have already used the TNG simulations to make predictions for astronomical transient sources \citep[e.g.][]{Briel+2021,Bavera+2022}. In particular, \cite{Briel+2021} show that the \SFRDzZ from the TNG and the EAGLE \citep{Schaye+2015,Crain+2015} simulations provide the best agreement between observed and predicted cosmic rates for electromagnetic and gravitational-wave transients.

% Downsides of TNG100 
On the other hand, large uncertainties and crude approximations remain in all contemporary cosmological simulations, thus also in the TNG simulations. For example, dust is not included in the TNG simulations, which could mean that metallicity of the star-forming gas is overestimated. Furthermore, all mass loss from massive stellar winds \citep[e.g.][]{Dray+2003}, pair-pulsational supernovae \citep[e.g.][]{Renzo+2020} binary interactions \citep[e.g.][]{Farmer2021_carbonfootprint} and their ionising effects \citep[][]{Gotberg+2020,DoughtyFinlator2021} are ignored.  Moreover, the uniform ionising UV background is turned on abruptly at $z=6$, which crucially impacts the amount of low metallicity star formation at low redshift.

These large uncertainties call for a generalised form of the \SFRDzZ that can be easily updated when new information becomes available, which is the motivation for this work. Although here, we only fit our model to the TNG100 simulation, our prescription can be easily be used to fit other simulated data or observational data of the metallicity dependent star formation rate density \footnote{We provide a Jupyter notebook to facilitate this fit here \todo{add link}}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Choices and binning of the data}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We fit equation \ref{eq: total sfrd} to the metallicity-dependent star formation rate of the star-forming gas in the TNG100 simulation. For this we use a binned version of the TNG data $\SFRDzZ_{\rm sim}$. We consider metallicities between $Z= -5$ to $\log_{10} Z= 0$ in 30 bins, where we use $Z_i$ to refer to the logarithmic centres of the bins. We ignore star formation in metallicities $\log_{10} Z \le -5$ as this accounts for less than 1\% of the total cosmic star formation rate in these simulations.
We consider bins in redshifts between $z=0$ and $z=10$, with a step size of $dz=0.05$, where $z_j$ refers to the centres of the bins.

@@

Subsequently we sum the $\chi^2 (z_j)$ for all redshift bins $z_j$. To ensure that our fit procedure gives sufficient weight to the behaviour at all redshifts, we find that we need to introduce a penalisation factor to somewhat reduce the contribution of redshifts where the peak of cosmic star formation occurs, while increasing the weight where at redshifts where the overall cosmic star formation rate is lower.  To achieve this we divide $\chi^2 (z_j)$ by the star formation $\sum_{Z_i} \mathcal{S}(Z_i,z_j)$ per redshift bin before adding the contribution of all redshifts.  Our final expression for the cost function reads

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Resulting \SFRDzZ}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Our best fitting parameters are listed in Table \ref{tab: fit params}. With these fit parameters, $\chi^2(z_j)$ is smaller than $2\cdot 10^{-4}$ at any given redshift. We will refer to the \SFRDzZ with the parameters listed in Table \ref{tab: fit params} as our fiducial model. 
% With the fit parameters as mentioned above, we find a maximum residual between the model and the TNG100 data of $2.3\cdot 10^{-3} \Msun \yr^{-1} \Mpc^{-3}$ at any given redshift.

@@

In Figure \ref{fig: fit SFRD} we show our fiducial  model at different redshifts and metallicities. For clarity, we also show the overall rate of star formation \SFRDz in Figure \ref{fig: SFR(z)}.
In general, our analytical model captures the metallicity dependent star formation in the TNG100 simulations well (bottom panels of Figure \ref{fig: fit SFRD}). 
The skewed-log normal metallicity distribution is able to reproduce the overall behaviour that is observed in TNG100 \citep[bottom left panel, but cf. ][for an in-depth discussion of low metallicity star formation in the TNG50 simulation]{Pakmor+2022}.
Only minor features like the additional bump just above $\log_{10}(Z) = -2$ at redshift 2 are missed. 
However, for our purposes, it is more important to prioritise fitting the large scale trends, while we are not so interested in smaller scale fluctuations.

Adopting a skewed-lognormal metallicity distribution allows for a tail of low metallicity star formation out to low redshifts. To emphasise the difference between a skewed-lognormal and a symmetric lognormal distribution, we show the phenomenological model from \cite{Neijssel+2019} in dotted grey. Their model falls within the family of functions that is encompassed by our model described in Section \ref{sec: model for sfrd(zZ)}. \footnote{The phenomenological model from \cite{Neijssel+2019} is recovered by adopting $\mu_0= 0.035$, $\mu_z=-0.23$, $\omega_0=0.39 $, $\omega_z = 0$, $\alpha = 0$, $a=0.01$, $b=2.77$, $c=2.9$ and $d=4.7$. }
% The \SFRDzZ from \cite{Neijssel+2019} was optimised to match the local rate of double compact object mergers as presented in the second gravitational-wave catalogue. However, the resulting symmetric distribution cuts-off virtually all low-metallicity ($Z\leq 10^{-2.5}$) star formation.

% For both \SFRDzZ distributions, most star formation happens at metallicities above $Z \geq 10^{-2}$ (top panel).

@@

% The paramters that affect the redshift evolution change the slope of high mass BHs
Parameters that change the evolution of the metallicity distribution \dpdZ with redshift, such as $\omega_z$ and $\mu_z$ (top right and centre right panel), primarily affect the slope of the high mass end of the BBH mass distribution.
By reducing the amount of low-metallicity star formation at high redshifts, formation channels with long delay times are excluded. In these simulations, the higher mass systems come from the `stable mass transfer channel' which is characterised by longer delay times \citep[][see also their Figure 6]{vanson+2022}.  
% This is similar to the redshift evolution of the mass distribution as discussed in \cite{vanson+2022} (Figure 6). 
% The difference between the effect on the low mass end with respect to the high mass end of the mass distribution is largest for these variations.
